A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Add two words that James can't do

\paragraph{Label classes} We require only $\BigO{g+h}$ space per level of the
search tree to store labelling information.  This is done by storing a
\emph{label class} as a pair $\langle \setG,\setH \rangle$ for each label $l$ that is
used, where $\setG$ is the set of vertices in $\V(\graphG)$ labelled $l$, and $\setH$ is the
set of vertices in $\V(\graphH)$ labelled $l$. Since there are $g + h$ vertices in the two graphs, at most
$g + h$ label classes can exist at once, and there are at most $g + h$ vertices
in the union of all of the $\setG$ and $\setH$ sets. Furthermore, we do not actually
need to store the bits making up a label---we care only that like-labelled
vertices are kept together, and the label itself is not used. Nor do we need to
store any label class which is present only in one graph but not the other (or
which is not present at all).  Together, these facts allow us to store all the
necessary information in two pairs of flat arrays. One pair of arrays is used
to store a permutation of the vertices in $\setG$ having like-labelled vertices
stored consecutively, together with the indices of the start of each label in
turn (in some arbitrary order). The second pair stores the permutation of
vertices in $\setH$, together with label start indices \emph{in the same order} as
they are used in the first pair of arrays. This representation has
similarities to data structures used in partition backtracking
\citep{DBLP:conf/wea/Lopez-PresaA09,DBLP:journals/jsc/McKayP14} and the \citet{DBLP:journals/cacm/BronK73}
clique enumeration algorithm.

>>>>

\paragraph{Label classes} We require only $\BigO{g+h}$ space per level of the
search tree to store labelling information.  This is done by storing a
\emph{label class} as a pair $\langle \setG,\setH \rangle$ for each label $l$ that is
used, where $\setG$ is the set of vertices in $\V(\graphG)$ labelled $l$, and $\setH$ is the
set of vertices in $\V(\graphH)$ labelled $l$. Since there are $g + h$ vertices in the two graphs, at most
$g + h$ label classes can exist at once, and there are at most $g + h$ vertices
in the union of all of the $\setG$ and $\setH$ sets. Furthermore, we do not actually
need to store the bits making up a label---we care only that like-labelled
vertices are kept together, and the label itself is not used. Nor do we need to
store any label class which is present only in one graph but not the other (or
which is not present at all).  Together, these facts allow us to store all the
necessary information in two pairs of flat arrays. One pair of arrays is used
to store a permutation of the vertices in $\setG$ having like-labelled vertices
stored consecutively, together with the size and indices of the start of each label in
turn (in some arbitrary order). The second pair stores the permutation of
vertices in $\setH$, together with label start indices \emph{in the same order} as
they are used in the first pair of arrays. This representation has
similarities to data structures used in partition backtracking
\citep{DBLP:conf/wea/Lopez-PresaA09,DBLP:journals/jsc/McKayP14} and the \citet{DBLP:journals/cacm/BronK73}
clique enumeration algorithm.
